Forecasting the black Sigatoka development rate: A comparison of machine learning techniques

### 2015-11-18 Paper Sigatoka - 2015.tex
miercoles medio dia

\usepackage{lineno,hyperref}
\modulolinenumbers[1]

@@

\subsubsection{Support Vector Regression (SVR)}
From the perspective of Support Vector Regression (SVR) the regression function $y = f(s)$ for a given dataset $D ={(s_i,y_i ) }_(i=1)^n$ , is represented as a linear function of the form (Wei, Tao, ZhuoShu, and Zio, 2013):
$f(s)=w^T s+b$
where 	$w$ and $b$ are respectively the weight vector and the intercept of the model, and they are selected to find an optimal fit to the data available in $D$.
For nonlinear cases, one proceeds by mapping the input p-dimensional vectors via a nonlinear function $ɸ∶R^p→F$, onto the feature space F.  After nonlinear mapping, the regression function evolves to a pervasive form:
$$f(s)=w^T ɸ(s)+b$$
SVR uses the є-insensitive loss function:
% $$l=|y-f(s)|_є= {(0,   |y-f(s)|_  ≤ є |y-f(s)|_ - є,     else)$$

which ignores the error if the difference between the prediction value and the actual value is smaller than $є$.
$є-insensitive loss function$ allows to find the coefficients $w$ and $b$ by solving a convex optimization problem, which balances the empirical error and the generalization ability. In SVR, the empirical error is measured by the loss function є-insensitive and the generalization ability is measured by the Euclidean norm of $w$. Then, the optimization problem to identify the regression model can be formulated by (Wei, Tao, ZhuoShu, and Zio, 2013):
% $minimize    J(w,ξ_i,ξ_i^* )=  1/2  ||w| |^2+ C ∑_(i=1)^n▒〖(ξ_i,ξ_i^*)〗
% subject to 	{█(y_i- w^T  ɸ(s)-b  ≤   є+ξ_i@w^T  ɸ(s)+b- y_i   ≤   є% 
% +ξ_i^*     i=1,…,n@ξ_i,ξ_i^(* )≥0)┤$
where C denotes the penalty parameter between empirical and generalization errors, and  $ξ_i,ξ_i^(* )$are slack variables, as shown in Fig 2.

@@

>>>>

\usepackage{lineno,hyperref}

\usepackage{amsmath}

\modulolinenumbers[1]

@@

\subsubsection{Support Vector Regression (SVR)}
From the perspective of Support Vector Regression (SVR) the regression function $y = f(s)$ for a given dataset $D=\{(s_i,y_i)\}_{i=1}^n$ , is represented as a linear function of the form \citep{Wei2013}:

$$f(s)=w^Ts+b$$

where $w$ and $b$ are respectively the weight vector and the intercept of the model, and they are selected to find an optimal fit to the data available in $D$.

For nonlinear cases, one proceeds by mapping the input p-dimensional vectors via a nonlinear function $\phi : R^p\rightarrow F$, onto the feature space $F$.  After nonlinear mapping, the regression function evolves to a pervasive form:

$$f(s)=w^T \phi (s)+b$$

SVR uses the $ \epsilon -insensitive \ loss \ function$:

\[l= {\Bigr| y - f(s) \Bigr| }_{\epsilon } = 
\left\{\begin{array}{lcl}
	0 & \mbox{} & {\Bigr| y - f(s) \Bigr| } \leq \epsilon \\
	 &  & \\
	{\Bigr| y - f(s) \Bigr| - \epsilon} & \mbox{} & else\\ \end{array} \right. \]

which ignores the error if the difference between the prediction value and the actual value is smaller than $ \epsilon$.
The $ \epsilon -insensitive \ loss \ function$ allows to find the coefficients $w$ and $b$ by solving a convex optimization problem, which balances the empirical error and the generalization ability. In SVR, the empirical error is measured by the loss function є-insensitive and the generalization ability is measured by the Euclidean norm of $w$ \citep{XXXX201X}. Then, the optimization problem to identify the regression model can be formulated by \citep{Wei2013}:

\begin{equation} 
\begin{aligned}
& \underset{}{\text{miimize}}
& & J(w,\xi_i , \xi_i^* ) = \frac{1}{2}   \Bigr| \Bigr| x \Bigr| \Bigr|^2 + C \sum_{i=1}^{n} (\xi_i , \xi_i^* )    \\
& \text{subject to}
& & \begin{array}{lcl} 
y_i - w^T \phi (s) - b  \leq \epsilon + \xi_i   \\
w^T \phi (s) + b - y_i \leq \epsilon + \xi_i^* & i= 1,2,...,n \\
\xi_i , \xi_i^* \geq 0  \\
\end{array}
\end{aligned}
\end{equation}  
where $C$ denotes the penalty parameter between empirical and generalization errors, and  $\xi_i , \xi_i^*$ are slack variables. \figurename
$.$\ref{figura2} shows this situation.

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.9]{SVR}
 \caption{$\epsilon -insensitive \ loss \ function \citep{Wei2013}.$} 
 \label{figura2} 
\end{figure}

@@

\bibitem[Wei et al., 2013]{Wei2013} Wei, Z., Tao, T., ZhuoShu, D.,  Zio, E. (2013). A dynamic particle filter-support vector regression method for reliability prediction. Reliability Engineering \& System Safety, 109–116. doi:10.1016/j.ress.2013.05.021.

\bibitem[Libro SVM XXXX, 201X]{XXXX201X} Libro SVM XXXX.
